### 2020-02-13 README.Rmd
Add buffer for SCBI

**EDA of both BigWoods & SCBI**: Note the large variation in growths for the SCBI trees over the BigWoods trees.

@@

```{r, cache = TRUE}
```

>>>>

@@

```{r, cache = TRUE}
scbi_boundary <- tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  sf_polygon()

# Buffer polygon
scbi_buffer <- scbi_boundary %>%
  st_buffer(dist = -max_dist)

# Sample of 5000 trees
set.seed(76)
scbi_trees_sample <- scbi_growth_df %>% 
  sample_n(5000) %>% 
  select(x = gx, y = gy) %>% 
  st_as_sf(coords = c("x", "y"))

index <- st_intersects(scbi_trees_sample, scbi_buffer, sparse = FALSE)
scbi_trees_sample <- scbi_trees_sample %>% 
  mutate(buffer = index)

# Plot
ggplot() +
  geom_sf(data = scbi_boundary) +
  geom_sf(data = scbi_buffer, col="red") +
  geom_sf(data = scbi_trees_sample, aes(col=buffer), size = 0.5)
```
